% !TEX root = ./amsa_main.tex
\subsubsection{Second-Order Cone Programming}\label{sec:socp}
SOCP extends LP by incorporating second-order cones. A second-order cone in $\RR^n$ is $$Q=\big\{(x_1,x_2,\ldots,x_n)\in\RR^n:\|(x_2,\ldots,x_n)\|_2\le x_1\big\}.$$  
Given a point $v\in\RR^n$, let  $\rho_1^v:=\|(v_2,\ldots,v_n)\|_2$ and $\rho_2^v:=\frac{1}{2}(v_1+\rho_1^v)$}. Then, the projection {of  $v$ to $Q$ {returns $0$ if $v_1<-\rho_1$, returns $v$ if $v_1 \ge \rho_1$, and returns $(\rho_2^v,\frac{\rho_2^v}{\rho_1^v}\cdot(v_2,\ldots,v_n))$ otherwise. Therefore, if we define the scalar couple:
$$(\xi_1^v,\xi_2^v) = \begin{cases}(0,0),&\quad v_1<-\rho_2^v\\
(1,1), &\quad v_1 \ge \rho_2^v\\
\big(\rho_2^v,\frac{\rho_2^v}{\rho_1^v}\big),&\quad \mbox{otherwise}\end{cases}
$$
then we have $u=\Proj_{Q}(v) = \big(\xi_1 ^vv_1,\,\xi_2^v\cdot (v_2,\ldots,v_n)\big)$. Based on this, we have 
\begin{proposition}\label{prop:socproj}
\begin{enumerate}
\item Let $v\in\RR^{n}$ and $v^+ := v+ (\boldsymbol e_i)\nu$ for any $\nu\in\RR$. Then, given $\rho_1^v,\rho_2^v,\xi_1^v,\xi_2^v$ {defined above}, it takes $O(1)$ operations to obtain $\rho_1^{v^+},\rho_2^{v^+},\xi_1^{v^+},\xi_2^{v^+}$. 
\item Let $v\in\RR^{n}$ and $A=[a_1~A_2]\in\RR^{m\times n}$, where $a_1\in\RR^m,A_2\in\RR^{m\times (n-1)}$. Given $\rho_1^v,\rho_2^v,\xi_1^v,\xi_2^v$, we have $$A(2\cdot\Proj_{Q}(v)-I)=((2\xi_1 ^v-1)v_1)\cdot a_1 + (2\xi_2-1)\cdot A_2 (v_2,\ldots,v_n)^T.$$
\end{enumerate}
\end{proposition}
By the proposition, if $\cT_1$ is an affine operator, then in the composition $\cT_1\circ \Proj_{Q}$, {the computation of $\Proj_{Q}$ is cheap as long as we maintain $\rho_1^v,\rho_2^v,\xi_1^v,\xi_2$.

Given $x,c\in\RR^n$, $b\in\RR^m$, and $A\in\RR^{m\times n}$, the standard-form SOCP is
\begin{subequations}\label{eq:socp}
\begin{align}
\Min_x~c^\top x,&\quad\St~ Ax=b\\
&\hspace{56pt} x\in X=Q_1\times \cdots\times Q_{\bar{n}}
\end{align}
\end{subequations}
where each $Q_i$ is a second-order cone, and $\bar{n}\not=n$ in general.
The problem \eqref{eq:socp} is equivalent to 
$$\Min_x \big(c^\top  x+\iota_{A\cdot =b}(x)\big)+\iota_X(x),$$
to which we can apply the DRS iteration $z^{k+1} = \TDRS (z^k)$ (see \eqref{eq:DRS}), in which $\cT_1 = \Proj_X$ and $\cT_2$ is a linear operator given by 
$$\cT_2(x) = \argmin_y ~ c^\top y+\frac{1}{2}y^\top Cy +  \frac{1}{2\gamma}\|y-x\|^2\quad \St~ Ax=b.$$
Assume that the matrix $A$ has full row-rank (otherwise, $Ax=b$ has either redundant rows or no solution). 
Then, in \eqref{eq:DRS}, we have $\cR_{\cT_2}(x)= Bx+d$, where $B:=\cI-2A^\top (AA^\top )^{-1}A$ and $d:=2A^\top (AA^\top )^{-1}(b+\gamma Ac)-2\gamma c$.

It is easy to apply coordinate updates to $z^{k+1} = \TDRS (z^k)$ following Proposition \ref{prop:socproj}. Specifically, by maintaining the scalars $\rho_1^v,\rho_2^v,\xi_1^v,\xi_2^v$ for each $v=x_i\in Q_i$ during  coordinate updates, the computation of the projection can be completely avoided. We pre-compute $(AA^\top )^{-1}$ and cache the matrix $B$ and vector $d$. Then, $\TDRS$ is CF. 

It trivial to extend this method for  SOCPs with a quadratic objective:
\begin{align*}
\Min_x~c^\top x+\frac{1}{2}x^\top Cx,&\quad\St~ Ax=b,~ x\in X=Q_1\times \cdots\times Q_{\bar{n}}
\end{align*}
because $\cT_2$ is still linear.  Clearly, this method applies to linear programs as they are special SOCPs.

Note that many LPs and SOCPs have sparse matrices $A$, which deserve further investigation. In particular, we may prefer not to form $(AA^\top )^{-1}$ and use the results in \S\ref{sec:emp} instead.

\cut{
\subsection{SOCP by primal-dual coordinate update}
SOCP can be viewed as an extended monotropic programming problem $\eqref{emp}$, as illustrated in section $\ref{sec:emp}$. So it can be solved by using $\eqref{pdemp}$ with a dual variable $s$:
\begin{equation}
\left\{
\begin{array}{l}
s^{k+1}=s^k+\gamma (Ax^k-b)\\
x^{k+1}=\Proj_{Q_1\times\cdots\times Q_{\bar{n}}}(x^k-\eta(c+A^\top s^k+2\gamma A^\top Ax^k-2\gamma A^\top b))
\end{array}
\right.,
\end{equation}
which is CF.
\subsection{Conic programming self-dual embedding}
Self-dual embedding reduces a pair of primal dual conic programs to a single convex feasibility problem. Unlike the previous approach, which focuses on solving either the primal or dual problem, operator splitting can be applied to solve the single feasibility problem. When the problem is optimal, it will return a solution; otherwise, it will return a certificate that proves either primal or dual infeasibility. Self-dual embedding was introduced in \cite{?} and led to solvers in \cite{?,?}. In particular, the solver SCS ....
\subsection{Quadratic programming}
The quadratic programming $\eqref{qp}$ 
\begin{equation}
\underset{x\in\mathbb{R}^m}{\text{minimize }} \frac{1}{2}x^\top Ux+c^\top x,\text{ subject to } Ax=b,~x\in X,
\end{equation}
where $U$ is a positive semidefinite matrix, $X=\{x:x_i \geq 0,\forall i\geq j\}$, can be viewed as $\eqref{emp}$ and solved by using $\eqref{pdemp}$ with a dual variable $s$:
\begin{equation}
\left\{
\begin{array}{l}
s^{k+1}=s^k+\gamma (Ax^k-b)\\
x^{k+1}=\Proj_{X}(x^k-\eta(Ux^k+c+A^\top s^k+2\gamma A^\top Ax^k-2\gamma A^\top b))
\end{array}
\right.,
\end{equation}
which is CF since $\Proj_X$ belongs to $\cC_1$.
}
